Section_8_Team1_Lab2_Report

### 2021-08-04 notebooks/Draft_Report.Rmd
moved Rmd to /notebooks and set pdf report output to /report. set path to processed csv.

#we may not need all of these
library(tidyverse)
library(magrittr)
library(ggplot2)
library(patchwork)
library(sandwich)
library(lmtest)
library(dplyr)
library(table1)
library(GGally)
library(stargazer)
theme_set(theme_minimal())
knitr::opts_chunk$set(echo = TRUE)

@@

```{r dataframe, echo=FALSE}
df <- read.csv('~/lab-2-lab2_section8_jal/data/interim/covid_trips_interim_model3.csv')
#head(df)
```

@@

```{r EDA, echo=FALSE, message=FALSE}
#Example Table
df$rural_cat <- ifelse(df$is_rural == 1, "Rural Counties", "Urban Counties")
table1::label(df$total_pop) <- "County Population"
table1::label(df$density) <- "County Population Density"
table1::label(df$cases) <- "County Covid-19 Cases"
table1::label(df$unempoy_rate) <- "County Unemployment Rate"
table1::label(df$median_income) <- "County Median Income ($)"
table1::label(df$pct_lt17) <- "County Age < 17 years (%)"
table1::label(df$pct_gt65) <- "County Age > 65 years (%)"
# table1::label(df$is_rural) <- "County Type"
table1::table1(~total_pop + density + cases + unempoy_rate + median_income + pct_lt17 + pct_gt65 | rural_cat, data = df, caption = "Table 1: Texas County Variable Statistics", topclass="Rtable1-zebra", overall = "Total")

@@

df %>%
  mutate(
    total_pop = log(total_pop),
    cases = log(cases+1),
    deaths = log(deaths+1),
    long_trip = log(long_trip),
    density = log(density)
  ) %>%
  select(long_trip, cases, deaths, median_income, unempoy_rate, density, pct_lt17) %>%
  GGally::ggpairs(.,
               legend = 1, title = "Figure 1: Variable Statistics",
               mapping = ggplot2::aes(colour=Rural_County))

@@

#need to change these to per capita data
model1 <- lm(log(long_trip) ~ log(cases+1) + log(deaths+1) + is_rural + median_income, data = df) #limited model
model2 <- lm(log(long_trip) ~ log(cases+1) + log(deaths+1) + is_rural + median_income + unempoy_rate + log(density), data = df)
model3 <- lm(log(long_trip) ~ log(cases+1) + log(deaths+1) + is_rural + median_income + unempoy_rate + log(density) + pct_lt17 + pct_gt65, data = df) #final model

>>>>

#we may not need all of these
library(tidyverse)
library(magrittr)
library(ggplot2)
library(patchwork)
library(sandwich)
library(lmtest)
library(dplyr)
library(table1)
library(GGally)
library(stargazer)
theme_set(theme_minimal())
knitr::opts_chunk$set(echo = TRUE)
knitr::knit(output = "./../reports/final_report.pdf")
```

@@

```{r dataframe, echo=FALSE}
df <- read.csv('./../data/processed/covid_trips_processed.csv')
#head(df)
```

@@

```{r EDA, echo=FALSE, message=FALSE}
#Example Table
df$rural_cat <- ifelse(df$is_rural == 1, "Rural Counties", "Urban Counties")
table1::label(df$total_pop) <- "County Population"
table1::label(df$density) <- "County Population Density"
table1::label(df$cases) <- "County Covid-19 Cases"
table1::label(df$unemp_rate) <- "County Unemployment Rate"
table1::label(df$median_income) <- "County Median Income ($)"
table1::label(df$pct_lt17) <- "County Age < 17 years (%)"
table1::label(df$pct_gt65) <- "County Age > 65 years (%)"
# table1::label(df$is_rural) <- "County Type"
table1::table1(~total_pop + density + cases + unemp_rate + median_income + pct_lt17 + pct_gt65 | rural_cat, data = df, caption = "Table 1: Texas County Variable Statistics", topclass="Rtable1-zebra", overall = "Total")

@@

df %>%
  mutate(
    total_pop = log(total_pop),
    cases = log(cases+1),
    deaths = log(deaths+1),
    long_trip = log(long_trip),
    density = log(density)
  ) %>%
  select(long_trip, cases, deaths, median_income, unemp, density, pct_lt17) %>%
  GGally::ggpairs(.,
               legend = 1, title = "Figure 1: Variable Statistics",
               mapping = ggplot2::aes(colour=Rural_County))

@@

#need to change these to per capita data
model1 <- lm(log(long_trip) ~ log(cases+1) + log(deaths+1) + is_rural + median_income, data = df) #limited model
model2 <- lm(log(long_trip) ~ log(cases+1) + log(deaths+1) + is_rural + median_income + unemp + log(density), data = df)
model3 <- lm(log(long_trip) ~ log(cases+1) + log(deaths+1) + is_rural + median_income + unemp + log(density) + pct_lt17 + pct_gt65, data = df) #final model
